---
title: "Analysis Final"
author: "Michael Lombardo"
date: "30/4/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prepare dataset

```{r, warning=FALSE, message=FALSE}
library(easypackages)
libraries("here","tidyverse","foreign","lmerTest","psych",
          "ggeasy","emmeans","patchwork","reshape2")

codepath = here("code")
source(file.path(codepath,"utils.R"))
datapath = here("data")
plotpath = here("plots")
resultpath = here("results")

fontSize = 24
cols2use = c("#619cff","#ffa500")

data_fname = file.path(datapath, "MIRA dataset 10-21-23.sav")
tidy_data = prep_dataset(data_fname)
```

# Contingency tables describing data

```{r, warning=FALSE, message=FALSE}
#  Sex x Treatment Type
table(tidy_data$sex,tidy_data$tx)

# Responder Status
table(tidy_data$responder15)
table(tidy_data$responder24)

# Responder Status x Treatment Type
table(tidy_data$responder15,tidy_data$tx)
table(tidy_data$responder24,tidy_data$tx)

# Responder Status x Sex
table(tidy_data$responder15,tidy_data$sex)
table(tidy_data$responder24,tidy_data$sex)

# Responder Status x Treatment ESDM vs Other
table(tidy_data$responder15,tidy_data$tx_mvl)
table(tidy_data$responder24,tidy_data$tx_mvl)

# Responder Status x Treatment Type (Broad)
table(tidy_data$responder15,tidy_data$tx_broad)
table(tidy_data$responder24,tidy_data$tx_broad)
```

# Preprocess data before modeling

The continuous predictors in the model should be scaled (e.g., z-scored) first.

```{r, warning=FALSE, message=FALSE}
categorical_predictors = c("tx_broad","sex")

# scale predictors as a pre-processing step for the continuous variables that will be modeled
continuous_predictors = c("age_at_start",
                          "tx_duration",
                          "intensity",
                          "pre_imitation",
                          "pre_vabs_abc",
                          "pre_ados_css",
                          # "pretx_dq",
                          "pretx_verbal_dq",
                          "pretx_nonverbal_dq")

pcavars = c("age_at_start","tx_duration","intensity",
            "pre_imitation",
            "pre_vabs_abc",
            "pre_ados_css",
            "pretx_verbal_dq",
            "pretx_nonverbal_dq")
```

# Acquisition of phrase speech

IVs: sex + tx_broad + age_at_start + intensity + pre_imitation + pre_vabs_abc + pre_ados_css + pretx_verbal_dq + pretx_nonverbal_dq

RFX: (1 | dataset)

```{r, warning=FALSE, message=FALSE}
responder_var = "responder24"

# Responder Status x Treatment Type (Broad)
tmp_tbl = table(tidy_data[,responder_var],tidy_data$tx_broad)
print(tmp_tbl)

max2use = max(tmp_tbl)
data2plot = data.frame(t(tmp_tbl))
# cols2use = get_ggColorHue(4)

tx_label2use = "ESDM"
p_esdm = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle(tx_label2use) + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

tx_label2use = "EIBI"
p_eibi = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle(tx_label2use) + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

tx_label2use = "NDBI"
p_ndbi = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle(tx_label2use) + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

tx_label2use = "Other"
p_other = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle("Classroom-Based") + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

p_final = p_esdm + p_ndbi + p_eibi + p_other + plot_layout(nrow=2,ncol=2)
ggsave(filename = file.path(plotpath, "tx_sample_size_24mo.pdf"), plot = p_final,
       width = 16, height=10)
p_final


# Correlation matrix after using only subjects with complete responder18 labels
mask = rowSums(is.na(tidy_data[,c(responder_var,continuous_predictors)]))==0
data2use = tidy_data %>% filter(mask)

corr_mat = cor(data2use[,continuous_predictors], use="pairwise.complete.obs")
dist = as.dist((1-corr_mat)/2)
hc = hclust(dist)
corr_mat = corr_mat[hc$order, hc$order]
data2plot = melt(corr_mat)
# colnames(data2plot)[3] = "r"
p = ggplot(data = data2plot, aes(x = Var1, y = Var2, fill = value, label = round(value,2))) +
  geom_tile() +
  geom_text() + 
  labs(x = NULL, y = NULL, fill = "r") +
  scale_fill_gradientn(colours = colorRampPalette(c("blue","white","red"))(100), 
                       limits = c(-1,1), 
                       oob = scales::squish) +
  scale_x_discrete(labels = c("Duration", "VABS ABC","Verbal DQ","Nonverbal DQ", 
                              "ADOS CSS", "Imitation","Age at Start","Intensity")) +
  scale_y_discrete(labels = c("Duration", "VABS ABC","Verbal DQ","Nonverbal DQ", 
                              "ADOS CSS", "Imitation","Age at Start","Intensity")) + 
  ggtitle("Predictor Variable Correlations") + 
  easy_center_title() +  
  theme_minimal() +
  theme(axis.text.x = element_text(hjust = 0.95),
        axis.text.y = element_text(hjust = 0.95),
        plot.title = element_text(hjust = 0.5),
        legend.title.align=0.22)

p = p + easy_rotate_x_labels(angle = 90) +
  theme(axis.text.y = element_text(hjust = 0.95), 
        axis.text.x = element_text(hjust = 0.95),
        legend.title.align=0.22)
ggsave(filename = file.path(plotpath, "24mo_corrmat.pdf"), plot = p)
p
        

# run again with PCA on continuous predictors
form2use = as.formula(sprintf("%s ~ sex + tx_broad + PC1 + PC2 + PC3 + PC4 + PC5 + (1 | dataset)",responder_var))

# fit model
result = logistic_regression(data = tidy_data, 
                             formula = form2use, 
                             vars2scale = continuous_predictors, 
                             responder_var = responder_var,
                             do_pca = TRUE,
                             pcavars = pcavars,
                             recon_pcs = c("PC1","PC2"))
# pairwise comparisons of tx_broad
pairwise_res = emmeans(result$model, pairwise ~ tx_broad)
pairwise_res

summary(result$pca_res)

data2plot = result$pca_res$rotation[hc$order,]
data2plot = melt(data2plot)
p = ggplot(data = data2plot, aes(x = Var2, y = Var1, fill = value, label = round(value,2))) +
  geom_tile() +
  geom_text() + 
  labs(x = NULL, y = NULL, fill = "Loading") +
  scale_fill_gradientn(colours = colorRampPalette(c("blue","white","red"))(100), 
                       limits = c(-0.5,0.5), 
                       oob = scales::squish) +
  scale_x_discrete(labels = colnames(result$pca_res$rotation)) +
  scale_y_discrete(labels = rev(c("Intensity","Age at Start","Imitation","ADOS CSS", 
                              "Nonverbal DQ","Verbal DQ","VABS ABC","Duration"))) + 
  ggtitle("PCA Loadings") + 
  easy_center_title() +  
  theme_minimal() +
  theme(axis.text.y = element_text(hjust = 0.95),
        plot.title = element_text(hjust = 0.5))
ggsave(filename = file.path(plotpath, "24mo_pcaloadings.pdf"), plot = p)
p

# plot screeplot
pca_res = prcomp(data2use[,pcavars], scale=TRUE)
data2plot = data.frame(comps = colnames(pca_res$rotation),
           percent_var = ((pca_res$sdev^2) / sum(pca_res$sdev^2)) * 100)
p = ggplot(data = data2plot, aes(x = comps, y = percent_var)) + 
  geom_point() + 
  geom_line(aes(group=1)) + 
  xlab("Components") + ylab("Percentage Variance Explained") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, size=fontSize),
      strip.text.y = element_text(size=fontSize),
      axis.text.x = element_text(size=fontSize),
      axis.text.y = element_text(size=fontSize-2),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size=fontSize),
      strip.text = element_text(size = fontSize))
ggsave(filename = file.path(plotpath,"24mo_screeplot.pdf"), plot = p)
p

# Plot the PCs by responder status
data2plot = result$data
vars2plot = c("PC1","PC2")
for (var2plot in vars2plot){
  p = ggplot(data = data2plot, aes(x = .data[[responder_var]], 
                                    y = .data[[var2plot]], 
                                    colour = .data[[responder_var]])) + 
    geom_scatterbox() + ggtitle(var2plot) + easy_center_title()
  print(p)
  
  d_res = cohens_d(x = data2plot[data2plot[,responder_var]=="Responder", var2plot], 
           y = data2plot[data2plot[,responder_var]=="Non-Responder", var2plot])
  print(sprintf("Effect size for %s is d = %f", var2plot, d_res))
}


# plot recon data retaining PC1 and PC2
tmp_res = logistic_regression(data = tidy_data, 
                             formula = form2use, 
                             vars2scale = continuous_predictors, 
                             responder_var = responder_var,
                             do_pca = TRUE,
                             pcavars = pcavars,
                             recon_pcs = c("PC1","PC2"),
                             print_output = FALSE)
data2plot = tmp_res$pca_recon_data

vars2plot = c("age_at_start","tx_duration","intensity",
              "pre_imitation","pre_vabs_abc","pre_ados_css",
              "pretx_verbal_dq","pretx_nonverbal_dq")
varnames2use = c("Age at Start","Treatment Duration","Treatment Intensity",
              "Imitation","VABS ABC","ADOS CSS",
              "Verbal DQ","Nonverbal DQ")
i = 0
plots2save = list()
for (var2plot in vars2plot){
  i = i+1
  p = ggplot(data = data2plot, aes(x = .data[[responder_var]], 
                                    y = .data[[var2plot]], 
                                    colour = .data[[responder_var]])) + 
    # geom_scatterbox() + 
    geom_jitter(size=10) +
    geom_boxplot(fill = NA, colour = "#000000", outlier.shape = NA) +
    ylab(varnames2use[i]) + 
    scale_colour_manual(values=cols2use) + 
    scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
    guides(colour="none") +
    ggtitle(varnames2use[i]) + easy_center_title() + 
    easy_remove_x_axis(what = "title") + 
    theme_bw() + 
    theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
      strip.text.y = element_text(size=fontSize),
      axis.text.x = element_text(size=fontSize),
      axis.text.y = element_text(size=fontSize-2),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size=fontSize),
      strip.text = element_text(size = fontSize))
  ggsave(filename = file.path(plotpath,sprintf("%s_24mo_reconplot.pdf",var2plot)), plot = p)
  plots2save[[i]] = p
  print(p)
  
  d_res = cohens_d(x = data2plot[data2plot[,responder_var]=="Responder", var2plot], 
         y = data2plot[data2plot[,responder_var]=="Non-Responder", var2plot])
  print(sprintf("Effect size for %s is d = %f", var2plot, d_res))
}

p_final = plots2save[[1]] + plots2save[[3]] + plots2save[[6]] + plots2save[[4]] + plots2save[[5]] + plots2save[[8]] + plots2save[[7]] + plots2save[[2]] + plot_layout(nrow = 2, ncol = 4)
ggsave(filename = file.path(plotpath,"24mo_reconplot.pdf"), plot = p_final, 
       width = 24, height=15)
p_final
```

# Acquisition of single words

IVs: sex + tx_broad + age_at_start + intensity + pre_imitation + pre_vabs_abc + pre_ados_css + pretx_verbal_dq + pretx_nonverbal_dq

RFX: (1 | dataset)

```{r, warning=FALSE, message=FALSE}
responder_var = "responder15"

# Responder Status x Treatment Type (Broad)
tmp_tbl = table(tidy_data[,responder_var],tidy_data$tx_broad)
print(tmp_tbl)

max2use = max(tmp_tbl)
data2plot = data.frame(t(tmp_tbl))
# cols2use = get_ggColorHue(4)

tx_label2use = "ESDM"
p_esdm = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle(tx_label2use) + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

tx_label2use = "EIBI"
p_eibi = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle(tx_label2use) + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

tx_label2use = "NDBI"
p_ndbi = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle(tx_label2use) + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

tx_label2use = "Other"
p_other = ggplot(data = data2plot[data2plot$Var1==tx_label2use,], aes(x=Var2,y=Freq)) + 
  geom_bar(stat="identity",aes(fill = Var2)) + 
  xlab("Responder Type") + 
  ylab("Sample Size") + ylim(0,max2use) + 
  scale_fill_manual(values=cols2use) + 
  scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
  theme_bw() + 
  guides(fill="none") +
  ggtitle("Classroom-Based") + 
  easy_center_title() +  
  theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
    strip.text.y = element_text(size=fontSize),
    axis.text.x = element_text(size=fontSize),
    axis.text.y = element_text(size=fontSize-2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=fontSize),
    strip.text = element_text(size = fontSize))

p_final = p_esdm + p_ndbi + p_eibi + p_other + plot_layout(nrow=2,ncol=2)
ggsave(filename = file.path(plotpath, "tx_sample_size_15mo.pdf"), plot = p_final,
       width = 16, height = 10)
p_final


# Correlation matrix after using only subjects with complete responder18 labels
mask = rowSums(is.na(tidy_data[,c(responder_var,continuous_predictors)]))==0
data2use = tidy_data %>% filter(mask)

corr_mat = cor(data2use[,continuous_predictors], use="pairwise.complete.obs")
dist = as.dist((1-corr_mat)/2)
hc = hclust(dist)
corr_mat = corr_mat[hc$order, hc$order]
data2plot = melt(corr_mat)
# colnames(data2plot)[3] = "r"
p = ggplot(data = data2plot, aes(x = Var1, y = Var2, fill = value, label = round(value,2))) +
  geom_tile() +
  geom_text() + 
  labs(x = NULL, y = NULL, fill = "r") +
  scale_fill_gradientn(colours = colorRampPalette(c("blue","white","red"))(100), 
                       limits = c(-1,1), 
                       oob = scales::squish) +
  scale_x_discrete(labels = c("Imitation", "Duration","VABS ABC","Verbal DQ", 
                              "Nonverbal DQ", "ADOS CSS","Age at Start","Intensity")) +
  scale_y_discrete(labels = c("Imitation", "Duration","VABS ABC","Verbal DQ", 
                              "Nonverbal DQ", "ADOS CSS","Age at Start","Intensity")) +
  ggtitle("Predictor Variable Correlations") + 
  easy_center_title() +  
  theme_minimal() +
  theme(axis.text.x = element_text(hjust = 0.95),
        axis.text.y = element_text(hjust = 0.95), 
        plot.title = element_text(hjust = 0.5),
        legend.title.align=0.22)

p = p + easy_rotate_x_labels(angle = 90) +
  theme(axis.text.y = element_text(hjust = 0.95), 
        axis.text.x = element_text(hjust = 0.95),
        legend.title.align=0.22)
ggsave(filename = file.path(plotpath, "15mo_corrmat.pdf"), plot = p)
p


# run again with PCA on continuous predictors
form2use = as.formula(sprintf("%s ~ sex + tx_broad + PC1 + PC2 + PC3 + PC4 + PC5 + (1 | dataset)",responder_var))

# fit model
result = logistic_regression(data = tidy_data, 
                             formula = form2use, 
                             vars2scale = continuous_predictors, 
                             responder_var = responder_var,
                             do_pca = TRUE,
                             pcavars = pcavars,
                             recon_pcs = c("PC1","PC2"))
# pairwise comparisons of tx_broad
pairwise_res = emmeans(result$model, pairwise ~ tx_broad)
pairwise_res

summary(result$pca_res)

data2plot = result$pca_res$rotation[hc$order,]
data2plot = melt(data2plot)
p = ggplot(data = data2plot, aes(x = Var2, y = Var1, fill = value, label = round(value,2))) +
  geom_tile() +
  geom_text() + 
  labs(x = NULL, y = NULL, fill = "Loading") +
  scale_fill_gradientn(colours = colorRampPalette(c("blue","white","red"))(100), 
                       limits = c(-0.5,0.5), 
                       oob = scales::squish) +
  scale_x_discrete(labels = colnames(result$pca_res$rotation)) +
  scale_y_discrete(labels = rev(c("Intensity","Age at Start","ADOS CSS","Nonverbal DQ",
                              "Verbal DQ","VABS ABC","Duration","Imitation"))) + 
  ggtitle("PCA Loadings") + 
  easy_center_title() +  
  theme_minimal() +
  theme(axis.text.y = element_text(hjust = 0.95),
        plot.title = element_text(hjust = 0.5))
ggsave(filename = file.path(plotpath, "15mo_pcaloadings.pdf"), plot = p)
p

# plot screeplot
pca_res = prcomp(data2use[,pcavars], scale=TRUE)
data2plot = data.frame(comps = colnames(pca_res$rotation),
           percent_var = ((pca_res$sdev^2) / sum(pca_res$sdev^2)) * 100)
p = ggplot(data = data2plot, aes(x = comps, y = percent_var)) + 
  geom_point() + 
  geom_line(aes(group=1)) + 
  xlab("Components") + ylab("Percentage Variance Explained") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, size=fontSize),
      strip.text.y = element_text(size=fontSize),
      axis.text.x = element_text(size=fontSize),
      axis.text.y = element_text(size=fontSize-2),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size=fontSize),
      strip.text = element_text(size = fontSize))
ggsave(filename = file.path(plotpath,"15mo_screeplot.pdf"), plot = p)
p

# Plot the PCs by responder status
data2plot = result$data
vars2plot = c("PC2","PC4")
for (var2plot in vars2plot){
  p = ggplot(data = data2plot, aes(x = .data[[responder_var]], 
                                    y = .data[[var2plot]], 
                                    colour = .data[[responder_var]])) + 
    geom_scatterbox() + ggtitle(var2plot) + easy_center_title()
  print(p)
  
  d_res = cohens_d(x = data2plot[data2plot[,responder_var]=="Responder", var2plot], 
           y = data2plot[data2plot[,responder_var]=="Non-Responder", var2plot])
  print(sprintf("Effect size for %s is d = %f", var2plot, d_res))
}

# plot recon data retaining PC2 and PC4
tmp_res = logistic_regression(data = tidy_data, 
                             formula = form2use, 
                             vars2scale = continuous_predictors, 
                             responder_var = responder_var,
                             do_pca = TRUE,
                             pcavars = pcavars,
                             recon_pcs = c("PC2","PC4"),
                             print_output = FALSE)
data2plot = tmp_res$pca_recon_data


vars2plot = c("age_at_start","tx_duration","intensity",
              "pre_imitation","pre_vabs_abc","pre_ados_css",
              "pretx_verbal_dq","pretx_nonverbal_dq")
varnames2use = c("Age at Start","Treatment Duration","Treatment Intensity",
              "Imitation","VABS ABC","ADOS CSS",
              "Verbal DQ","Nonverbal DQ")
i = 0
plots2save = list()
for (var2plot in vars2plot){
  i = i+1
  p = ggplot(data = data2plot, aes(x = .data[[responder_var]], 
                                    y = .data[[var2plot]], 
                                    colour = .data[[responder_var]])) + 
    # geom_scatterbox() + 
    geom_jitter(size=10) +
    geom_boxplot(fill = NA, colour = "#000000", outlier.shape = NA) +
    ylab(varnames2use[i]) + 
    scale_colour_manual(values=cols2use) + 
    scale_x_discrete(labels = c("Non-Advancer", "Advancer")) +
    guides(colour="none") +
    ggtitle(varnames2use[i]) + easy_center_title() + 
    easy_remove_x_axis(what = "title") + 
    theme_bw() + 
    theme(plot.title = element_text(hjust = 0.5, size=fontSize+8),
      strip.text.y = element_text(size=fontSize),
      axis.text.x = element_text(size=fontSize),
      axis.text.y = element_text(size=fontSize-2),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size=fontSize),
      strip.text = element_text(size = fontSize))
  ggsave(filename = file.path(plotpath,sprintf("%s_15mo_reconplot.pdf",var2plot)), plot = p)
  plots2save[[i]] = p
  print(p)
  
  d_res = cohens_d(x = data2plot[data2plot[,responder_var]=="Responder", var2plot], 
         y = data2plot[data2plot[,responder_var]=="Non-Responder", var2plot])
  print(sprintf("Effect size for %s is d = %f", var2plot, d_res))
}

p_final = plots2save[[1]] + plots2save[[3]] + plots2save[[6]] + plots2save[[4]] + plots2save[[5]] + plots2save[[8]] + plots2save[[7]] + plots2save[[2]] + plot_layout(nrow = 2, ncol = 4)
ggsave(filename = file.path(plotpath,"15mo_reconplot.pdf"), plot = p_final, 
       width = 24, height=15)
p_final
```
